Commutative $\Nat$-polyregular functions

### 2024-01-31 globals/metadata.tex
avancées
writing to publish
lipics compiles

\title{
    Star-free $\Nat$-polyregular functions:
    the commutative case.
}
\author{
    Aliaume Lopez
}
\affiliation{%
  \institution{Univeristy of Warsaw}
  \city{Warsaw}
  \country{Poland}}
\email{ad.lopez@uw.edu.pl}

\date{\today}
\bibliography{globals/papers}

\newcommand{\acknowledge}{
    I would like to thank 
    Anonymous Author(s)
    %Gaëtan Douéneau-Tabot
    for mentioning this problem, checking 
    my counter-example, and supporting me in publishing
    this paper.
}

@@

\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

>>>>

\date{\today}

\title{Commutative $\Nat$-polyregular functions}

\author{Aliaume Lopez}%
       {University of Warsaw}%
       {ad.lopez@uw.edu.pl}%
       {https://orcid.org/0000-0002-1825-0097}%
       {Gaëtan Douéneau-Tabot}

\authorrunning{A. Lopez}

%\titlerunning{Commutative $\Nat$-polyregular functions}
\date{\today}

\Copyright{Copyright Holder Name}

%TODO mandatory; please add comma-separated list of keywords
\keywords{Dummy keyword} 
\category{} %optional, e.g. invited paper
\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website

\newcommand{\acknowledge}{
    Acknowledge Gaëtan
}

@@

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
